\documentclass[journal,12pt,twocolumn]{IEEEtran}

\usepackage{setspace}
\usepackage{gensymb}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}
\singlespacing


\usepackage[cmex10]{amsmath}

\usepackage{amsthm}

\usepackage{mathrsfs}
\usepackage{txfonts}
\usepackage{stfloats}
\usepackage{bm}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}

\usepackage{longtable}
\usepackage{multirow}

\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{steinmetz}
\usepackage{tikz}
\usepackage{circuitikz}
\usepackage{verbatim}
\usepackage{tfrupee}
\usepackage[breaklinks=true]{hyperref}
\usepackage{graphicx}
\usepackage{tkz-euclide}

\usetikzlibrary{calc,math}
\usepackage{listings}
    \usepackage{color}                                            %%
    \usepackage{array}                                            %%
    \usepackage{longtable}                                        %%
    \usepackage{calc}                                             %%
    \usepackage{multirow}                                         %%
    \usepackage{hhline}                                           %%
    \usepackage{ifthen}                                           %%
    \usepackage{lscape}     
\usepackage{multicol}
\usepackage{chngcntr}

\DeclareMathOperator*{\Res}{Res}

\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\renewcommand\thesubsubsection{\thesubsection.\arabic{subsubsection}}

\renewcommand\thesectiondis{\arabic{section}}
\renewcommand\thesubsectiondis{\thesectiondis.\arabic{subsection}}
\renewcommand\thesubsubsectiondis{\thesubsectiondis.\arabic{subsubsection}}


\hyphenation{op-tical net-works semi-conduc-tor}
\def\inputGnumericTable{}                                 %%

\lstset{
%language=C,
frame=single, 
breaklines=true,
columns=fullflexible
}
\begin{document}


\newtheorem{theorem}{Theorem}[section]
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}{Example}[section]
\newtheorem{definition}[problem]{Definition}

\newcommand{\BEQA}{\begin{eqnarray}}
\newcommand{\EEQA}{\end{eqnarray}}
\newcommand{\define}{\stackrel{\triangle}{=}}
\bibliographystyle{IEEEtran}
\providecommand{\mbf}{\mathbf}
\providecommand{\pr}[1]{\ensuremath{\Pr\left(#1\right)}}
\providecommand{\qfunc}[1]{\ensuremath{Q\left(#1\right)}}
\providecommand{\sbrak}[1]{\ensuremath{{}\left[#1\right]}}
\providecommand{\lsbrak}[1]{\ensuremath{{}\left[#1\right.}}
\providecommand{\rsbrak}[1]{\ensuremath{{}\left.#1\right]}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\providecommand{\lbrak}[1]{\ensuremath{\left(#1\right.}}
\providecommand{\rbrak}[1]{\ensuremath{\left.#1\right)}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\lcbrak}[1]{\ensuremath{\left\{#1\right.}}
\providecommand{\rcbrak}[1]{\ensuremath{\left.#1\right\}}}


\theoremstyle{remark}
\newtheorem{rem}{Remark}
\newcommand{\sgn}{\mathop{\mathrm{sgn}}}
\providecommand{\abs}[1]{\left\vert#1\right\vert}
\providecommand{\res}[1]{\Res\displaylimits_{#1}} 
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
%\providecommand{\norm}[1]{\lVert#1\rVert}
\providecommand{\mtx}[1]{\mathbf{#1}}
\providecommand{\mean}[1]{E\left[ #1 \right]}
\providecommand{\fourier}{\overset{\mathcal{F}}{ \rightleftharpoons}}
%\providecommand{\hilbert}{\overset{\mathcal{H}}{ \rightleftharpoons}}
\providecommand{\system}{\overset{\mathcal{H}}{ \longleftrightarrow}}
	%\newcommand{\solution}[2]{\textbf{Solution:}{#1}}
\newcommand{\solution}{\noindent \textbf{Solution: }}
\newcommand{\cosec}{\,\text{cosec}\,}
\providecommand{\dec}[2]{\ensuremath{\overset{#1}{\underset{#2}{\gtrless}}}}
\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\newcommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\numberwithin{equation}{subsection}
\makeatletter
\@addtoreset{figure}{problem}
\makeatother
\let\StandardTheFigure\thefigure
\let\vec\mathbf
\renewcommand{\thefigure}{\theproblem}
\def\putbox#1#2#3{\makebox[0in][l]{\makebox[#1][l]{}\raisebox{\baselineskip}[0in][0in]{\raisebox{#2}[0in][0in]{#3}}}}
     \def\rightbox#1{\makebox[0in][r]{#1}}
     \def\centbox#1{\makebox[0in]{#1}}
     \def\topbox#1{\raisebox{-\baselineskip}[0in][0in]{#1}}
     \def\midbox#1{\raisebox{-0.5\baselineskip}[0in][0in]{#1}}
\vspace{3cm}
\title{Beacon Tracking using Arduino}
\author{Sachinkumar Dubey}
\maketitle
\newpage
\bigskip
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\tableofcontents
\newpage
\section{ALGORITHM-1}
\subsection{\textbf{Components}}
\url{https://github.com/sachinomdubey/Arduino/blob/main/Beacon\%20Tracking/Algorithm\%201/Component\%20List.pdf}
\subsection{\textbf{Wiring Diagram}}
\url{https://github.com/sachinomdubey/Arduino/blob/main/Beacon%20Tracking/Algorithm%201/Figures/Wiring%20Diagram.pdf}
\subsection{\textbf{Codes}}
\subsubsection{\textbf{ESP32 code}}
\begin{itemize}
    \item Connect the ESP32 board to Laptop/PC using Type-B USB cable.
    \item Open the \href{https://github.com/sachinomdubey/Arduino/blob/main/Beacon%20Tracking/Algorithm%201/Codes/Algorithm1_ESP32.ino}{Algorithm1\_ESP32.ino} file in Arduino IDE. 
    \item From Tools menu, select suitable "Board" and "Port" for your ESP32 board.
    \item Compile the code by clicking on "Verify" option.
    \item Upload the code to ESP32 using the "Upload" option.
\end{itemize}
\subsubsection{\textbf{Arduino code:}}
\begin{itemize}
    \item Connect the Arduino uno board to Laptop/PC using USB cable.
    \item Open the \href{https://github.com/sachinomdubey/Arduino/blob/main/Beacon%20Tracking/Algorithm%201/Codes/Algorithm1_Arduino.ino}{Algorithm1\_Arduino.ino} file in Arduino IDE. 
    \item From Tools menu, select Board as "Arduino Uno" and suitable "Port" on which the Arduino board is connected.
    \item Compile the code by clicking on "Verify" option.
    \item Upload the code to ESP32 using the "Upload" option.
\end{itemize}
\subsection{\textbf{Working}}
\begin{enumerate}
    \item Initially, ESP32 mounted on the car will read RSSI (Radio Signal Strength Indicator) levels in forward, right and left direction by suitable in-place rotation.
    \item Average of 20 RSSI values are taken while measuring RSSI level in a particular direction. This is done in order to read accurate RSSI levels.
    \item The car then rotates towards the direction having the highest RSSI level.
    \item Further, It moves forward with a distance depending on the free space available in front of it. The free space in front of the car is measured using ultrasonic sensor.
    \item By repeating above steps again and again, the car navigates towards the beacon.
\end{enumerate}
\subsection{\textbf{Observation/Conclusion}}
\begin{itemize}
    \item The algorithm described above is very basic and crude way to navigate toward the beacon. Frequent left and right rotation is required to identity the direction having the maximum RSSI level.
    \item Using this algorithm, only 60-70 percent of the time (i.e. 60-70\% Accuracy), the car rotates and moves towards the correct direction. Due to low accuracy, The car may take time to reach till the beacon. 
\end{itemize}
\end{document}