\abstract{
\par This report is intended to serve as a concise and to-the-point report of my work on navigation and communication for UGV (Unmanned Ground Vehicles) and UAV (Unmanned Aerial Vehicles). This thesis report titled "Navigation and Communication of UGV/UAV" consists of two parts:
   \begin{itemize}
  \item The navigation part of this thesis includes utilization of various controllers to implement applications on UGV/UAV hardware kit.
  \item The communication part explores SATCOM for 5G which can be utilized to communicate with UAV or UGV. It also briefly examines the use of NBIoT.
  \end{itemize}
UGV and UAV hardware kits are ideal low-cost prototype systems for testing software before scaling it up and putting it on a real ground vehicle or a more complicated UAV system. 

The communication part introduces SATCOM and its need in terrestrial cellular network. It also describes various application where SATCOM can be utilized in UAV communication. This report also includes an experimental setup to demonstrate working of SATCOM with 5G network. As part of testing, A video streaming test is perform between the User Equipment (UE) and the 5G core network (5GC). The crucial part of the experiment was to emulate satellite link delays and analyse its effect on the performance of the software stack at the UE, gNB and 5GC.
	Embedded hardware/Software for navigation and communication technologies for UGV/UAV are covered thoroughly in this report. Both of these parts are very important in operation of a UAV and a ground vehicle.
}